Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-22 graph_housing_exp2_distr_8_5.tex
Change all plots from probability to probability density

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$H$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.0060) (2.5884,0.3850,0.0060) (2.5884,0.4460,0.0060) (1.1296,0.4460,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4460,0.0000) (2.5884,0.4460,0.0000) (2.5884,0.4485,0.0000) (1.1296,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4485,0.0000) (2.5884,0.4485,0.0000) (2.5884,0.4555,0.0000) (1.1296,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4555,0.0000) (2.5884,0.4555,0.0000) (2.5884,0.4620,0.0000) (1.1296,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4620,0.0025) (2.5884,0.4620,0.0025) (2.5884,0.4705,0.0025) (1.1296,0.4705,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4705,0.0040) (2.5884,0.4705,0.0040) (2.5884,0.4910,0.0040) (1.1296,0.4910,0.0040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.0000) (2.5884,0.4910,0.0000) (2.5884,0.4960,0.0000) (1.1296,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.0000) (2.5884,0.4960,0.0000) (2.5884,0.5015,0.0000) (1.1296,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5015,0.0000) (2.5884,0.5015,0.0000) (2.5884,0.5085,0.0000) (1.1296,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5085,0.0000) (2.5884,0.5085,0.0000) (2.5884,0.5165,0.0000) (1.1296,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5165,0.0215) (2.5884,0.5165,0.0215) (2.5884,0.5410,0.0215) (1.1296,0.5410,0.0215)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.0055) (2.5884,0.5410,0.0055) (2.5884,0.5485,0.0055) (1.1296,0.5485,0.0055)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5485,0.0070) (2.5884,0.5485,0.0070) (2.5884,0.5775,0.0070) (1.1296,0.5775,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5775,0.0645) (2.5884,0.5775,0.0645) (2.5884,0.6010,0.0645) (1.1296,0.6010,0.0645)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6010,0.0260) (2.5884,0.6010,0.0260) (2.5884,0.6070,0.0260) (1.1296,0.6070,0.0260)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6070,0.0085) (2.5884,0.6070,0.0085) (2.5884,0.6115,0.0085) (1.1296,0.6115,0.0085)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6115,0.0100) (2.5884,0.6115,0.0100) (2.5884,0.6190,0.0100) (1.1296,0.6190,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6190,0.0325) (2.5884,0.6190,0.0325) (2.5884,0.6275,0.0325) (1.1296,0.6275,0.0325)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6275,0.0060) (2.5884,0.6275,0.0060) (2.5884,0.6390,0.0060) (1.1296,0.6390,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.0210) (2.5884,0.6390,0.0210) (2.5884,0.6510,0.0210) (1.1296,0.6510,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.1560) (2.5884,0.6510,0.1560) (2.5884,0.8205,0.1560) (1.1296,0.8205,0.1560)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.0370) (2.5884,0.8205,0.0370) (2.5884,0.8710,0.0370) (1.1296,0.8710,0.0370)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.0775) (4.9150,0.3850,0.0775) (4.9150,0.4460,0.0775) (2.5884,0.4460,0.0775)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4460,0.0150) (4.9150,0.4460,0.0150) (4.9150,0.4485,0.0150) (2.5884,0.4485,0.0150)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4485,0.0050) (4.9150,0.4485,0.0050) (4.9150,0.4555,0.0050) (2.5884,0.4555,0.0050)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4555,0.0040) (4.9150,0.4555,0.0040) (4.9150,0.4620,0.0040) (2.5884,0.4620,0.0040)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4620,0.0080) (4.9150,0.4620,0.0080) (4.9150,0.4705,0.0080) (2.5884,0.4705,0.0080)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4705,0.0290) (4.9150,0.4705,0.0290) (4.9150,0.4910,0.0290) (2.5884,0.4910,0.0290)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.0095) (4.9150,0.4910,0.0095) (4.9150,0.4960,0.0095) (2.5884,0.4960,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.0025) (4.9150,0.4960,0.0025) (4.9150,0.5015,0.0025) (2.5884,0.5015,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5015,0.0410) (4.9150,0.5015,0.0410) (4.9150,0.5085,0.0410) (2.5884,0.5085,0.0410)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5085,0.0100) (4.9150,0.5085,0.0100) (4.9150,0.5165,0.0100) (2.5884,0.5165,0.0100)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5165,0.0605) (4.9150,0.5165,0.0605) (4.9150,0.5410,0.0605) (2.5884,0.5410,0.0605)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.0295) (4.9150,0.5410,0.0295) (4.9150,0.5485,0.0295) (2.5884,0.5485,0.0295)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5485,0.0095) (4.9150,0.5485,0.0095) (4.9150,0.5775,0.0095) (2.5884,0.5775,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5775,0.0105) (4.9150,0.5775,0.0105) (4.9150,0.6010,0.0105) (2.5884,0.6010,0.0105)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6010,0.0000) (4.9150,0.6010,0.0000) (4.9150,0.6070,0.0000) (2.5884,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6070,0.0000) (4.9150,0.6070,0.0000) (4.9150,0.6115,0.0000) (2.5884,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6115,0.0020) (4.9150,0.6115,0.0020) (4.9150,0.6190,0.0020) (2.5884,0.6190,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6190,0.0000) (4.9150,0.6190,0.0000) (4.9150,0.6275,0.0000) (2.5884,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6275,0.0020) (4.9150,0.6275,0.0020) (4.9150,0.6390,0.0020) (2.5884,0.6390,0.0020)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.0015) (4.9150,0.6390,0.0015) (4.9150,0.6510,0.0015) (2.5884,0.6510,0.0015)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.0295) (4.9150,0.6510,0.0295) (4.9150,0.8205,0.0295) (2.5884,0.8205,0.0295)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.0000) (4.9150,0.8205,0.0000) (4.9150,0.8710,0.0000) (2.5884,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.3850,0.1245) (12.1265,0.3850,0.1245) (12.1265,0.4460,0.1245) (4.9150,0.4460,0.1245)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4460,0.0135) (12.1265,0.4460,0.0135) (12.1265,0.4485,0.0135) (4.9150,0.4485,0.0135)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4485,0.0160) (12.1265,0.4485,0.0160) (12.1265,0.4555,0.0160) (4.9150,0.4555,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4555,0.0090) (12.1265,0.4555,0.0090) (12.1265,0.4620,0.0090) (4.9150,0.4620,0.0090)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4620,0.0120) (12.1265,0.4620,0.0120) (12.1265,0.4705,0.0120) (4.9150,0.4705,0.0120)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4705,0.0185) (12.1265,0.4705,0.0185) (12.1265,0.4910,0.0185) (4.9150,0.4910,0.0185)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4910,0.0030) (12.1265,0.4910,0.0030) (12.1265,0.4960,0.0030) (4.9150,0.4960,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4960,0.0070) (12.1265,0.4960,0.0070) (12.1265,0.5015,0.0070) (4.9150,0.5015,0.0070)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5015,0.0000) (12.1265,0.5015,0.0000) (12.1265,0.5085,0.0000) (4.9150,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5085,0.0200) (12.1265,0.5085,0.0200) (12.1265,0.5165,0.0200) (4.9150,0.5165,0.0200)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5165,0.0160) (12.1265,0.5165,0.0160) (12.1265,0.5410,0.0160) (4.9150,0.5410,0.0160)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5410,0.0000) (12.1265,0.5410,0.0000) (12.1265,0.5485,0.0000) (4.9150,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5485,0.0060) (12.1265,0.5485,0.0060) (12.1265,0.5775,0.0060) (4.9150,0.5775,0.0060)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5775,0.0000) (12.1265,0.5775,0.0000) (12.1265,0.6010,0.0000) (4.9150,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6010,0.0000) (12.1265,0.6010,0.0000) (12.1265,0.6070,0.0000) (4.9150,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6070,0.0000) (12.1265,0.6070,0.0000) (12.1265,0.6115,0.0000) (4.9150,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6115,0.0000) (12.1265,0.6115,0.0000) (12.1265,0.6190,0.0000) (4.9150,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6190,0.0000) (12.1265,0.6190,0.0000) (12.1265,0.6275,0.0000) (4.9150,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6275,0.0000) (12.1265,0.6275,0.0000) (12.1265,0.6390,0.0000) (4.9150,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6390,0.0000) (12.1265,0.6390,0.0000) (12.1265,0.6510,0.0000) (4.9150,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6510,0.0000) (12.1265,0.6510,0.0000) (12.1265,0.8205,0.0000) (4.9150,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.8205,0.0000) (12.1265,0.8205,0.0000) (12.1265,0.8710,0.0000) (4.9150,0.8710,0.0000)};

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=H,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=0.4,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.08,...,0.41},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.3850,0.006743) (2.5884,0.3850,0.006743) (2.5884,0.4460,0.0067) (1.1296,0.4460,0.0067)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4460,0.000000) (2.5884,0.4460,0.000000) (2.5884,0.4485,0.0000) (1.1296,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4485,0.000000) (2.5884,0.4485,0.000000) (2.5884,0.4555,0.0000) (1.1296,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4555,0.000000) (2.5884,0.4555,0.000000) (2.5884,0.4620,0.0000) (1.1296,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4620,0.020162) (2.5884,0.4620,0.020162) (2.5884,0.4705,0.0202) (1.1296,0.4705,0.0202)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4705,0.013376) (2.5884,0.4705,0.013376) (2.5884,0.4910,0.0134) (1.1296,0.4910,0.0134)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4910,0.000000) (2.5884,0.4910,0.000000) (2.5884,0.4960,0.0000) (1.1296,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.4960,0.000000) (2.5884,0.4960,0.000000) (2.5884,0.5015,0.0000) (1.1296,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5015,0.000000) (2.5884,0.5015,0.000000) (2.5884,0.5085,0.0000) (1.1296,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5085,0.000000) (2.5884,0.5085,0.000000) (2.5884,0.5165,0.0000) (1.1296,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5165,0.060158) (2.5884,0.5165,0.060158) (2.5884,0.5410,0.0602) (1.1296,0.5410,0.0602)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5410,0.050271) (2.5884,0.5410,0.050271) (2.5884,0.5485,0.0503) (1.1296,0.5485,0.0503)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5485,0.016547) (2.5884,0.5485,0.016547) (2.5884,0.5775,0.0165) (1.1296,0.5775,0.0165)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.5775,0.188153) (2.5884,0.5775,0.188153) (2.5884,0.6010,0.1882) (1.1296,0.6010,0.1882)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6010,0.297058) (2.5884,0.6010,0.297058) (2.5884,0.6070,0.2971) (1.1296,0.6070,0.2971)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6070,0.129487) (2.5884,0.6070,0.129487) (2.5884,0.6115,0.1295) (1.1296,0.6115,0.1295)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6115,0.091402) (2.5884,0.6115,0.091402) (2.5884,0.6190,0.0914) (1.1296,0.6190,0.0914)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6190,0.262110) (2.5884,0.6190,0.262110) (2.5884,0.6275,0.2621) (1.1296,0.6275,0.2621)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6275,0.035766) (2.5884,0.6275,0.035766) (2.5884,0.6390,0.0358) (1.1296,0.6390,0.0358)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6390,0.119966) (2.5884,0.6390,0.119966) (2.5884,0.6510,0.1200) (1.1296,0.6510,0.1200)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.6510,0.063092) (2.5884,0.6510,0.063092) (2.5884,0.8205,0.0631) (1.1296,0.8205,0.0631)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(1.1296,0.8205,0.050226) (2.5884,0.8205,0.050226) (2.5884,0.8710,0.0502) (1.1296,0.8710,0.0502)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.3850,0.054607) (4.9150,0.3850,0.054607) (4.9150,0.4460,0.0546) (2.5884,0.4460,0.0546)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4460,0.257887) (4.9150,0.4460,0.257887) (4.9150,0.4485,0.2579) (2.5884,0.4485,0.2579)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4485,0.030701) (4.9150,0.4485,0.030701) (4.9150,0.4555,0.0307) (2.5884,0.4555,0.0307)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4555,0.026450) (4.9150,0.4555,0.026450) (4.9150,0.4620,0.0264) (2.5884,0.4620,0.0264)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4620,0.040453) (4.9150,0.4620,0.040453) (4.9150,0.4705,0.0405) (2.5884,0.4705,0.0405)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4705,0.060803) (4.9150,0.4705,0.060803) (4.9150,0.4910,0.0608) (2.5884,0.4910,0.0608)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4910,0.081664) (4.9150,0.4910,0.081664) (4.9150,0.4960,0.0817) (2.5884,0.4960,0.0817)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.4960,0.019537) (4.9150,0.4960,0.019537) (4.9150,0.5015,0.0195) (2.5884,0.5015,0.0195)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5015,0.251747) (4.9150,0.5015,0.251747) (4.9150,0.5085,0.2517) (2.5884,0.5085,0.2517)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5085,0.053726) (4.9150,0.5085,0.053726) (4.9150,0.5165,0.0537) (2.5884,0.5165,0.0537)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5165,0.106137) (4.9150,0.5165,0.106137) (4.9150,0.5410,0.1061) (2.5884,0.5410,0.1061)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5410,0.169059) (4.9150,0.5410,0.169059) (4.9150,0.5485,0.1691) (2.5884,0.5485,0.1691)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5485,0.014080) (4.9150,0.5485,0.014080) (4.9150,0.5775,0.0141) (2.5884,0.5775,0.0141)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.5775,0.019204) (4.9150,0.5775,0.019204) (4.9150,0.6010,0.0192) (2.5884,0.6010,0.0192)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6010,0.000000) (4.9150,0.6010,0.000000) (4.9150,0.6070,0.0000) (2.5884,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6070,0.000000) (4.9150,0.6070,0.000000) (4.9150,0.6115,0.0000) (2.5884,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6115,0.011462) (4.9150,0.6115,0.011462) (4.9150,0.6190,0.0115) (2.5884,0.6190,0.0115)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6190,0.000000) (4.9150,0.6190,0.000000) (4.9150,0.6275,0.0000) (2.5884,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6275,0.007475) (4.9150,0.6275,0.007475) (4.9150,0.6390,0.0075) (2.5884,0.6390,0.0075)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6390,0.005373) (4.9150,0.6390,0.005373) (4.9150,0.6510,0.0054) (2.5884,0.6510,0.0054)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.6510,0.007480) (4.9150,0.6510,0.007480) (4.9150,0.8205,0.0075) (2.5884,0.8205,0.0075)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(2.5884,0.8205,0.000000) (4.9150,0.8205,0.000000) (4.9150,0.8710,0.0000) (2.5884,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.3850,0.028302) (12.1265,0.3850,0.028302) (12.1265,0.4460,0.0283) (4.9150,0.4460,0.0283)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4460,0.074880) (12.1265,0.4460,0.074880) (12.1265,0.4485,0.0749) (4.9150,0.4485,0.0749)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4485,0.031695) (12.1265,0.4485,0.031695) (12.1265,0.4555,0.0317) (4.9150,0.4555,0.0317)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4555,0.019200) (12.1265,0.4555,0.019200) (12.1265,0.4620,0.0192) (4.9150,0.4620,0.0192)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4620,0.019576) (12.1265,0.4620,0.019576) (12.1265,0.4705,0.0196) (4.9150,0.4705,0.0196)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4705,0.012514) (12.1265,0.4705,0.012514) (12.1265,0.4910,0.0125) (4.9150,0.4910,0.0125)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4910,0.008320) (12.1265,0.4910,0.008320) (12.1265,0.4960,0.0083) (4.9150,0.4960,0.0083)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.4960,0.017648) (12.1265,0.4960,0.017648) (12.1265,0.5015,0.0176) (4.9150,0.5015,0.0176)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5015,0.000000) (12.1265,0.5015,0.000000) (12.1265,0.5085,0.0000) (4.9150,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5085,0.034667) (12.1265,0.5085,0.034667) (12.1265,0.5165,0.0347) (4.9150,0.5165,0.0347)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5165,0.009056) (12.1265,0.5165,0.009056) (12.1265,0.5410,0.0091) (4.9150,0.5410,0.0091)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5410,0.000000) (12.1265,0.5410,0.000000) (12.1265,0.5485,0.0000) (4.9150,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5485,0.002869) (12.1265,0.5485,0.002869) (12.1265,0.5775,0.0029) (4.9150,0.5775,0.0029)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.5775,0.000000) (12.1265,0.5775,0.000000) (12.1265,0.6010,0.0000) (4.9150,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6010,0.000000) (12.1265,0.6010,0.000000) (12.1265,0.6070,0.0000) (4.9150,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6070,0.000000) (12.1265,0.6070,0.000000) (12.1265,0.6115,0.0000) (4.9150,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6115,0.000000) (12.1265,0.6115,0.000000) (12.1265,0.6190,0.0000) (4.9150,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6190,0.000000) (12.1265,0.6190,0.000000) (12.1265,0.6275,0.0000) (4.9150,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6275,0.000000) (12.1265,0.6275,0.000000) (12.1265,0.6390,0.0000) (4.9150,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6390,0.000000) (12.1265,0.6390,0.000000) (12.1265,0.6510,0.0000) (4.9150,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.6510,0.000000) (12.1265,0.6510,0.000000) (12.1265,0.8205,0.0000) (4.9150,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(4.9150,0.8205,0.000000) (12.1265,0.8205,0.000000) (12.1265,0.8710,0.0000) (4.9150,0.8710,0.0000)};

### 2015-11-22 probability_plot_old/graph_auto_exp1_distr_1_3.tex
Change all plots from probability to probability density

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        % ylabel=marginal discrete probability,
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        ylabel=probability density,
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

### 2015-11-22 probability_plot_old/graph_auto_exp2_distr_1_3.tex
Change all plots from probability to probability density

	\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

	\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        ylabel=probability density,
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]
